# Interactive component

```{r}
library(plotly)
library(lubridate)
library(tidyverse)
library(gganimate)
library(hrbrthemes)
```

```{r}
accumulate_by <- function(dat, var) {
  var <- lazyeval::f_eval(var, dat)
  lvls <- plotly:::getLevels(var)
  dats <- lapply(seq_along(lvls), function(x) {
    cbind(dat[var %in% lvls[seq(1, x)], ], frame = lvls[[x]])
  })
  dplyr::bind_rows(dats)
}
mutate_data <- function(tibble, label){
  tibble %>%
    filter(year(date) >= 2014) %>% 
    mutate(year = year(date), date = year(date) + (month(date) - 1) / 12, label = label)  %>%
    count(date, repo, label) %>%
    pivot_wider(names_from = label, values_from = n)
}
commit <- read_csv("resources/data/commits.csv")
issue <- read_csv("resources/data/issues.csv")  
pull <- read_csv("resources/data/pull_requests.csv")  

data <- tibble(date = rep(seq(2014, 2022 - 1/12, 1/12), 2), 
               repo = rep(c("ggplot2", "plotly"), each = 96)) %>%
  full_join(mutate_data(commit, "commit")) %>%
  full_join(mutate_data(issue %>% rename(date = created_at), "issue")) %>%
  full_join(mutate_data(pull %>% rename(date = created_at), "pull_request")) %>%
  replace_na(list(commit = 0, issue = 0, pull_request = 0))
```

## How about seeing time trend in a dynamic way?

The line fluctuates during years and after 2018, ggplot2 is in the higher position for pull requests and issues.
```{r}
anim <- data %>% 
  pivot_longer(cols = c(commit, issue, pull_request), names_to = "category") %>%
  ggplot(aes(x = date, y = value, color = repo)) +
  geom_line() +
  geom_point() +
  facet_wrap(~category, ncol = 1, scale = "free_y") +
  theme_ipsum() +
  transition_reveal(date)
anim_save("resources/anim_linechart.gif", anim)
anim
```

## Look deep into the overview

We can choose the part to see the overview of time trends for these two packages. A decreasing trend for the commits of both packages over time. And an increasing trend for both packages in 2015. You can click the button on the left to see the line chart for commit, issue, and pull request.
```{r}
data <- tibble(date = rep(seq(2014, 2022 - 1/12, 1/12), 2), 
               repo = rep(c("ggplot2", "plotly"), each = 96)) %>%
  full_join(mutate_data(commit, "commit")) %>%
  full_join(mutate_data(issue %>% rename(date = created_at), "issue")) %>%
  full_join(mutate_data(pull %>% rename(date = created_at), "pull_request")) %>%
  replace_na(list(commit = 0, issue = 0, pull_request = 0))

updatemenus <- list(
  list(
    active = 0,
    type=  "buttons",
    x = -0.1,
    buttons = list(
      list(
        label = "commit",
        method = "update",
        args = list(list(visible = c(FALSE, FALSE, TRUE, TRUE, FALSE, FALSE)))
        ),
      list(
        label = "issue",
        method = "update",
        args = list(list(visible = c(FALSE, FALSE, FALSE, FALSE, TRUE, TRUE)))
        ),
      list(
        label = "pull",
        method = "update",
        args = list(list(visible = c(TRUE, TRUE, FALSE, FALSE, FALSE, FALSE)))
        )
    )
  )
)

fig <- data %>%
  plot_ly(
    split = ~repo,
    type = 'scatter',
    mode = 'lines'
  )
fig <- fig %>% add_lines(x = ~date, y = ~commit)
fig <- fig %>% add_lines(x = ~date, y = ~issue, visible = FALSE)
fig <- fig %>% add_lines(x = ~date, y = ~pull_request, visible = FALSE)
fig <- fig %>% layout(
  xaxis = list(
    title = "Date",
    zeroline = F
  ),
  yaxis = list(
    title = "count",
    zeroline = F
  ),
  updatemenus = updatemenus
) 
fig
```

